---
title: ''
output:
  pdf_document:
    fig_caption: no
    keep_tex: yes
  word_document: default
classoption: landscape
---

```{r setup, include=FALSE}
rm(list=ls())

knitr::opts_chunk$set(echo = TRUE)
library(magick)
library(webshot)
library(knitr)
library(kableExtra)
library(tidyverse)

# define data directory
datadir <- file.path('/Users/dhardy/Dropbox/r_data/easement-justice')

# webshot::install_phantomjs()
## https://haozhu233.github.io/kableExtra/save_kable_and_as_image.html
```
# Lowcountry EJ Results
# --
### Table 1. Conservation Reserves by Data Source. 
Square miles of conservation land with number of reserves in parentheses. All reported numbers are unfiltered from data source with the exception being multipart polygons clipped to the Lowcountry region. 
```{r, include = TRUE, echo=FALSE}

df <- read.csv(file.path(datadir, 'cl-stats-unfiltered.csv'))[-1] %>%
  rename(area = acres) %>%
  mutate(area = round(area * 0.0015625)) %>% ## acres to mi^2
  mutate(GA.Pvt = ifelse(conscat == 'Private' & state == 'GA', area, NA),
         GA.Pub = ifelse(conscat == 'Public' & state == 'GA', area, NA),
         SC.Pvt = ifelse(conscat == 'Private' & state == 'SC', area, NA),
         SC.Pub = ifelse(conscat == 'Public' & state == 'SC', area, NA)) %>%
    mutate(GA.PvtC = ifelse(conscat == 'Private' & state == 'GA', count, NA),
         GA.PubC = ifelse(conscat == 'Public' & state == 'GA', count, NA),
         SC.PvtC = ifelse(conscat == 'Private' & state == 'SC', count, NA),
         SC.PubC = ifelse(conscat == 'Public' & state == 'SC', count, NA)) %>%
  select(-count, -area, -state, -conscat) %>%
  mutate(source = as.character(source)) %>%
  mutate(source = if_else(source == 'nced', 'NCED', 
                          if_else(source == 'padus', 'PAD-US',
                                  if_else(source == 'tnc', 'SC-TNC', NULL)))) %>%
  group_by(source) %>%
  summarise(GA.Pvt = sum(GA.Pvt, na.rm=T),
    SC.Pvt = sum(SC.Pvt, na.rm=T),
    GA.Pub = sum(GA.Pub, na.rm=T),
    SC.Pub = sum(SC.Pub, na.rm=T),
    GA.PvtC = sum(GA.PvtC, na.rm=T),
    SC.PvtC = sum(SC.PvtC, na.rm=T),
    GA.PubC = sum(GA.PubC, na.rm=T),
    SC.PubC = sum(SC.PubC, na.rm=T)) %>%
  mutate(GA.Pvt = paste(GA.Pvt, " (", GA.PvtC, ")", sep = ""),
         SC.Pvt = paste(SC.Pvt, "(", SC.PvtC, ")", sep = ""),
         GA.Pub = paste(GA.Pub, " (", GA.PubC, ")", sep = ""),
         SC.Pub = paste(SC.Pub, " (", SC.PubC, ")", sep = "")) %>%
  select(source:SC.Pub)

## replace zeros
df[3,2] <- paste("--")
df[3,4] <- paste("--")

df[3,3] <- paste("",df[3,3],"*", sep = "")
df[2,4] <- paste("",df[2,4],"*", sep = "")
df[2,5] <- paste("",df[2,5],"*", sep = "")
df[1,2] <- paste("",df[1,2],"*", sep = "")

# helpful info on kable use: https://rpubs.com/yutao/444395

# LaTeX Table
kable(df, format = "latex", booktabs = T, caption = NULL,
      align = c("l", "c", "c", "c", "c"),
      col.names = c('Data\nSource', 'Georgia', 'South Carolina', 'Georgia', 'South Carolina')) %>%
  # kable_styling(full_width = NULL) %>%
  # row_spec(3, bold = T, hline_after = T) %>%
  add_header_above(c(" ", "Private" = 2, "Public" = 2)) %>%
  add_footnote(c("We only analyzed these reserves to minimize duplication from sources."), notation = "symbol") %>%
  as_image()
```

### Table 2. Demographic Comparison by Region. 
Results are from the 10 mile beneficiary zone and 0.2 mile conservation reserve buffer zone pairing. Standard error is shown for means of private and public beneficiary zones.
```{r include=TRUE, echo=FALSE}

df2 <- read.csv(file.path(datadir, 'regional-comparison.csv'))[-1] %>%
  mutate(id = if_else(region == "Lowcountry", 1, 
                      if_else(region == "South Carolina", 2, 3)),
         area = round(sqkm * 0.386102,0),
         se_area = round(se_sqkm * 0.386102,0),
         popden = round(popden * 0.386102), 0) %>%
  arrange(id, region, cat) %>%
  filter(region == 'Lowcountry') %>%
  mutate(area = paste0(area, " (± ", se_area, ")"),
         tot_pop = paste0(tot_pop, " (± ", se_tot_pop, ")"),
         popden = paste0(popden, " (± ", se_popden, ")"),
         pwhite = paste0(pwhite, " (± ", se_pwhite, ")"),
         pblack = paste0(pblack, " (± ", se_pblack, ")"),
         pother = paste0(pother, " (± ", se_pother, ")"),
         platinx = paste0(platinx, " (± ", se_platinx, ")"),
         propPOC = paste0(propPOC, " (± ", se_propPOC, ")"),
         medhhinc = paste0(medhhinc, " (± ", se_medhhinc, ")")) %>%
  mutate(urban = if_else(is.na(urban), .$urban[2] + .$urban[3], urban)) %>%
  # mutate(medhhinc = paste("$", medhhinc, sep = '')) %>%
  select(region, cat, area, tot_pop:pblack, medhhinc)

df2[1,3:9] <- str_remove(df2[1,3:9], " \\(± NA\\)")


# Other.exp <- expression(paste("Other (%)", a^2))

COLNAMES = c("Region", 'Area (mi²)', 'Beneficiary Population', 'Population (per mi²)', 'Urban Reserve Zones', 'White (%)', 'Black (%)', 'Median Income ($US)')

# LaTeX Table
df2 %>%
  select(-region) %>%
  kable(format = "latex", booktabs = T, caption = NULL,
        col.names = COLNAMES, align = "lccccccc") %>%
  # kable_styling(latex_options = "scale_down", "striped",
  #               full_width = NULL) %>%
  # pack_rows("Interstate", 1, 3) %>%
  # pack_rows("South Carolina", 4, 6) %>%
  # pack_rows("Georgia", 7, 9) %>%
  # add_footnote(c("Other includes Native American, Asian, Multiracial, and Other Race groups as defined in the U.S. Census.",
  #                "People of Color includes Black and Latinx plus our Other racial grouping."), notation = "alphabet") %>%
  as_image()
```
\pagebreak

### Table 2.1 (URBAN v. RURAL). Demographic Comparison by Region. 
Results are from the 10 mile beneficiary zone and 0.2 mile conservation reserve buffer zone pairing. Standard error is shown for means of private and public beneficiary zones.
```{r include=TRUE, echo=FALSE}

df2 <- read.csv(file.path(datadir, 'regional-comparison.csv'))[-1] %>%
  filter(!(region %in% c("Georgia", "South Carolina"))) %>%
  # group_by(region) %>%
  rename(reserves = urban) %>%
  mutate(id = if_else(cat == "Lowcountry", 1, 
                      if_else(region == "Private", 2, 3)),
         area = round(sqkm * 0.386102,0),
         se_area = round(se_sqkm * 0.386102,0),
         popden = round(popden * 0.386102, 0)) %>%
  arrange(id, cat, region) %>%
  mutate(reserves = ifelse(is.na(reserves), '1053', 
                           ifelse(region == "Lowcountry" & cat == "Private", .$reserves[3]+.$reserves[4],
                                  ifelse(region == "Lowcountry" & cat == "Public", .$reserves[6]+.$reserves[7],
                                         reserves)))) %>%
    mutate(area = paste0(area, " (± ", se_area, ")"),
         tot_pop = paste0(tot_pop, " (± ", se_tot_pop, ")"),
         popden = paste0(popden, " (± ", se_popden, ")"),
         pwhite = paste0(pwhite, " (± ", se_pwhite, ")"),
         pblack = paste0(pblack, " (± ", se_pblack, ")"),
         pother = paste0(pother, " (± ", se_pother, ")"),
         platinx = paste0(platinx, " (± ", se_platinx, ")"),
         propPOC = paste0(propPOC, " (± ", se_propPOC, ")"),
         medhhinc = paste0(medhhinc, " (± ", se_medhhinc, ")")) %>%
  select(region, cat, area, tot_pop:pblack, medhhinc)

df2[1,3:9] <- str_remove(df2[1,3:9], " \\(± NA\\)")

# Other.exp <- expression(paste("Other (%)", a^2))

COLNAMES = c("Region", 'Area (mi²)', 'Beneficiary Population', 'Population (per mi²)', 'Reserve Zones (#)', 'White (%)', 'Black (%)', 'Median Income ($US)')

# LaTeX Table
df2 %>%
  select(-cat) %>%
  kable(format = "latex", booktabs = T, caption = NULL,
         col.names = COLNAMES, align = c('lrrrrrrr')) %>%
  # kable_styling(latex_options = "scale_down", "striped",
  #               full_width = NULL) %>%
  pack_rows("Lowcountry", 1, 1) %>%
  pack_rows("Private", 2, 4) %>%
  pack_rows("Public", 5, 7) %>%
  # add_footnote(c("Other includes Native American, Asian, Multiracial, and Other Race groups as defined in the U.S. Census.",
  #                "People of Color includes Black and Latinx plus our Other racial grouping."), notation = "alphabet") %>%
  as_image(width = 9)
```
\pagebreak

### Table 2.2 (EXPANDED). Demographic Comparison by Region. 
Results are from the 10 mile beneficiary zone and 0.2 mile conservation reserve buffer zone pairing. Standard error is shown for means of private and public beneficiary zones.
```{r include=TRUE, echo=FALSE}

df2 <- read.csv(file.path(datadir, 'regional-comparison.csv'))[-1] %>%
  filter(!(region %in% c('Rural', 'Urban'))) %>%
  mutate(id = if_else(region == "Lowcountry", 1, 
                      if_else(region == "South Carolina", 2, 3)),
         area = round(sqkm * 0.386102,0),
         se_area = round(se_sqkm * 0.386102,0),
         popden = round(popden * 0.386102), 0) %>%
  arrange(id, region, cat) %>%
  mutate(urban = ifelse(region == 'Lowcountry' & cat == 'Lowcountry', .$urban[2]+.$urban[3],
                        ifelse(region == 'South Carolina' & cat == 'Lowcountry', .$urban[5]+.$urban[6],
                               ifelse(region == 'Georgia' & cat == 'Lowcountry', .$urban[8]+.$urban[9], urban)))) %>%
  # mutate(medhhinc = paste("$", medhhinc, sep = '')) %>%
    mutate(area = paste0(area, " (± ", se_area, ")"),
         tot_pop = paste0(tot_pop, " (± ", se_tot_pop, ")"),
         popden = paste0(popden, " (± ", se_popden, ")"),
         pwhite = paste0(pwhite, " (± ", se_pwhite, ")"),
         pblack = paste0(pblack, " (± ", se_pblack, ")"),
         pother = paste0(pother, " (± ", se_pother, ")"),
         platinx = paste0(platinx, " (± ", se_platinx, ")"),
         propPOC = paste0(propPOC, " (± ", se_propPOC, ")"),
         medhhinc = paste0(medhhinc, " (± ", se_medhhinc, ")")) %>%
  select(region, cat, area, tot_pop:medhhinc)

df2[1,3:12] <- str_remove(df2[1,3:12], " \\(± NA\\)")
df2[4,3:12] <- str_remove(df2[4,3:12], " \\(± NA\\)")
df2[7,3:12] <- str_remove(df2[7,3:12], " \\(± NA\\)")

# LaTeX Table
df2 %>%
  select(-region) %>%
  kable(format = "latex", booktabs = T, caption = NULL,
         col.names = c('Region', 'Area (mi²)', 'Beneficiary Population', 'Population (per mi²)', 'Urban Reserve Zones', 'White (%)', 'Black (%)', 'Latinx (%)', 'Other (%)^a', 'People of Color (%)^b', 'Median Income ($US)')) %>%
  # kable_styling(latex_options = "scale_down", "striped",
  #               full_width = NULL) %>%
  pack_rows("Interstate", 1, 3) %>%
  pack_rows("South Carolina", 4, 6) %>%
  pack_rows("Georgia", 7, 9) %>%
  add_footnote(c("Other includes Native American, Asian, Multiracial, and Other Race groups as defined in the U.S. Census.",
                 "People of Color includes Black and Latinx plus our Other racial grouping."), notation = "alphabet") %>%
  as_image(width = 9)
```
